A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-08 tex/sec3-defs.tex
[ tex ] Minor in S3

Having established generic definitions, we can now specify the simply typed $\lambda$-calculus and its bidirectional type system in \Cref{sec:key-ideas}---including raw terms, (bidirectional) typing derivations, and mode derivations---using just a pair of signatures $\Sigma_{\bto}$ and $\Omega^{\Leftrightarrow}_\Lambda$ where $\Omega^{\Leftrightarrow}_{\Lambda}$ consists of
\[
  \aritysymbol{\mathsf{abs}}{A , B}{[A]B^{\chk}}{(A \bto B)^{\chk}} \quad\text{and}\quad \aritysymbol{\mathsf{app}}{A, B}{(A \bto B)^{\syn}, A^{\chk}}{B^{\syn}}
\]
and $\Sigma_{\bto}$ is from \Cref{ex:type-signature-for-function-type}.
Moreover, we are able to reason about constructions and properties that hold for any bidirectional simple type system $(\Sigma, \Omega)$.

>>>>

\begin{example}\label{ex:signature-simply-typed-lambda}
Having established generic definitions, we can now specify the simply typed $\lambda$-calculus and its bidirectional type system---including raw terms, (bidirectional) typing derivations, and mode derivations---using just a pair of signatures $\Sigma_{\bto}$ (\Cref{ex:type-signature-for-function-type}) and $\Omega^{\Leftrightarrow}_\Lambda$ which consists of 
\[
  \aritysymbol{\mathsf{abs}}{A , B}{[A]B^{\chk}}{(A \bto B)^{\chk}} \quad\text{and}\quad \aritysymbol{\mathsf{app}}{A, B}{(A \bto B)^{\syn}, A^{\chk}}{B^{\syn}}.
\]
\end{example}
Moreover, we are able to reason about constructions and properties that hold for any bidirectional simple type system $(\Sigma, \Omega)$.
